### 2013-07-10 tests_Auto-Mpg.Rmd
minor stuff

source("gapolyfuncs.R")
report <- make.report(my.data, population=25, iterations=10)

@@

save(report, file="Auto-Mpg.Rda") # recover with load("Auto-Mpg.Rda")

@@

write.table(df, "Auto-Mpg.txt")

>>>>

source("gapolyfuncs.R")
report <- make.report(my.data, population=300, iterations=50)

@@

save(report, file="Auto-Mpg300.Rda") # recover with load("Auto-Mpg300.Rda")

@@

write.table(df, "Auto-Mpg300.txt")
